\PaperTitle

### 2024-05-04 Final_Report/paper.tex
added logistic regression png
Added table and paragraph to results section

@@

\subsection{Model Comparison and Evaluation Results}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=9cm]{Figures_and_Graphs/LogReg.png}
  \caption{Logistic Regression model structure example}
  \label{fig:RFExample}
\end{figure}

@@

\subsection{Model Comparison and Evaluation Results}
The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (80\%) and Macro F1 score (0.00). These results mean the model was the most effective at classifying the selected websites based on network packet data.
This displays the neural network is much more effective at representing complex relationships in the data than the other models.

  \begin{table}[!h]
    \begin{center}
    \caption{Accuracy and Macro F1 Scores for Each Model}
    \label{tab:results}
    \begin{tabular}{|c|c|c|}
      \hline
      Model & Accuracy & Macro F1 \\
      \hline
      Logistic Regression & 56\% & 0.00 \\
      K-Nearest Neighbors & 77\% & 0.00 \\
      Random Forest & 78\% & 0.00 \\
      Neural Network & 80\% & 0.00 \\
      \hline
    \end{tabular}
    \end{center}
  \end{table}
